Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-03-27 draft.tex
change key observations in section 5

In this section, we will verify the observations made in the previous section by experimenting with Workload \Rmnum{1 } running on our dragonfly network under different placement and routing configurations. By generating a synthetic application, we turn a ``bully" into a ``bullee".

@@

\subsection{Network Performance Analysis}

@@

\subsection{Individual Application Analysis}

@@

\subsection{Key Observations}
Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.

\emph{First, the placement \& routing configuration allows network resource sharing between concurrently running applications. Random placement enables the router sharing and adaptive routing enables local and global channel sharing.}

\emph{Second, there are difference in terms of communication intensity between concurrently running applications. In workload \Rmnum{1}, AMG has the least amount of communication traffic compared with MultiGrid and CrystalRouter and it become the ``bullee". In workload \Rmnum{2}, sAMG has the most amount of communication traffic, which makes it the ``bully". }

We can stop this ``bully" by making both conditions invalid.

\section{Stop the ``Bully"}

The solution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs. Using contiguous placement\& minimal routing could be a way avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion. It is also unrealistic to use different routing scheme for each application with regard to its communication intensity, since routing scheme is pre-configured in the system and can not be changed on the fly. However, the job placement can be versatile to assign different allocation (contiguous or random) to specific application.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:hyb-plcmt-amg-commtime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:hyb-plcmt-mg-commtime}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:hyb-plcmt-cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement\& routing configurations. \textbf{HM, HA, HPA} denote hybrid placement coupled with minimal, adaptive and progressive adaptive routing respectively. }
   \label{fig:hyb-plcmt-apps-commtime}
\end{figure*}

Thus, we propose the hybrid placement as a reconcile solution. In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation. We evaluate the performance of hybrid placement\&routing configurations with parallel Workload \Rmnum{1}. AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation. Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing schemes, together with other configurations.

@@

Our work different from the previous works in the following ways. First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system. Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload. We found that although random placement \& adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation. Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network status when application is running. The traffic and busy time of router's each link are valuable information for detailed analysis.

>>>>

In this section, we will verify the observations made in the previous section by experimenting with Workload \Rmnum{1 } running on dragonfly network under different placement and routing configurations. By generating a synthetic application, we turn the ``bully" into ``bullee".

@@

\subsection{Network Performance Analysis}
\label{sec: workload-2 network analysis}

@@

\subsection{Individual Application Analysis}
\label{sec: workload-2 app analysis}

@@

\subsection{Key Observations}

In summary, based on the results presented in section \ref{sec: workload-2 network analysis} and \ref{sec: workload-2 app analysis}, we have made the following observations.

%Our study with synthetic workload confirms that the ``bully" behavior among concurrently running applications would happen when two conditions are satisfied.

%\emph{First, the placement \& routing configuration allows network resource sharing between concurrently running applications. Random placement enables the router sharing and adaptive routing enables local and global channel sharing.}

\emph{The application becomes ``bully" only because it has more amount of data transfer compared with its concurrently running peers.} ``Bully" application takes advantage of the network resource belonging to other applications when network sharing is enabled in random placement and adaptive routing policy.

\emph{The communication-intensive is a relative metric between concurrently running jobs.} MultiGrid and CrystalRouter are the ``bully" in Workload \Rmnum{1} and they become the ``bullee" when running concurrently with sAMG in Workload \Rmnum{2}.

\section{Hybrid Job Placement}

The solution for preventing this ``bully" behavior is to avoid network sharing between concurrently running jobs. Using contiguous placement and minimal routing could be a way to avoid network sharing, but both the workload and network performance could suffer degradation due to local congestion. It is also unrealistic to use different routing scheme for each application with regard to its communication intensity, since routing scheme is pre-configured in the system and can not be changed on the fly. However, the job placement can be versatile to assign different allocation (contiguous or random) to specific application.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/amg/commtime}
        \caption{AMG Communication Time}
        \label{fig:hyb-plcmt-amg-commtime}
    \end{subfigure}\hfill
    \hspace{1em}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/mg/commtime}
        \caption{MG Communication Time}
        \label{fig:hyb-plcmt-mg-commtime}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[height=1.3 in]{hyb-plcmt/cr/commtime}
        \caption{CR Communication Time}
        \label{fig:hyb-plcmt-cr-commtime}
    \end{subfigure}%
   \caption{Application communication time. Three applications running concurrently on dragonfly network with different placement and routing configurations. \textbf{HM, HA, HPA} denote hybrid placement coupled with minimal, adaptive and progressive adaptive routing respectively. }
   \label{fig:hyb-plcmt-apps-commtime}
\end{figure*}

Thus, we propose the hybrid placement as a reconcile solution. In the hybrid placement, the less communication-intensive application will get contiguous allocation while the communication-intensive ones will get random allocation. We evaluate the performance of hybrid placement and routing configurations with parallel Workload \Rmnum{1}. AMG gets contiguous allocation, MultiGrid and CrystalRouter get random allocation. Figure \ref{fig:hyb-plcmt-apps-commtime} shows each application communication time when hybrid placement coupled with different routing schemes, together with other configurations.

@@

Our work different from the previous works in the following ways. First, instead of using synthetic workload that generated based on predefined communication patterns, our simulation is driven by real application traces collected from production system. Second, not only we care about the workload performance, but also we pay attention to each individual application in the workload. We found that although random placement coupled with adaptive routing can improve the workload performance, some specific application in the workload may suffer performance degradation. Third, with the sophisticated simulation tool CODES, we can not only get applications communication information, but also the insight about the network status when application is running. The traffic and busy time of router's each link are valuable information for detailed analysis.
